Random Forests", OAs

### 2024-07-03 src/la_RF_corrected.Rmd
corrected RF v2 LA

```{r}
n = 1 #number of unique postcodes. 
m = 12

@@

# df9610 %>% filter(V1.domain == 1) %>% 
#   left_join(lookup, by = "pc", suffix =c("","")) %>% 
#   filter(ladcd == "E08000006" & year == 2006) %>% 
#   group_by(pc) %>% 
#   summarise(n = n()) %>% 
#   arrange(desc(n))
# 
# df9610 %>% filter(pc == "M28 2SL" & year == 2006 & V1.domain == 1)

problem.pcs <- df9610 %>% filter(year > 1999 & year < 2011) %>% 
  group_by(pc, year) %>% 
  summarise(n = n()) %>%
  ungroup() %>% 
  # complete(pc, year) %>% 
  # replace(is.na(n), 0) %>% 
  arrange(desc(n)) %>% 
  pivot_wider(names_from = year, values_from = n, names_prefix = "n_") %>% 
  dplyr::select(pc, n_2000, n_2001, n_2002, n_2003, n_2004, n_2005, n_2006, n_2007, n_2008, n_2009, n_2010) %>% 
  slice_head(n=10) %>% 
  dplyr::select(pc)

# [1] "M28 2SL"  "SE24 9HP" "CV8 2ED"  "CW1 6GL"  "EC1V 4PY" "DE21 7BF" "E14 9SR"  "GL16 7YA" "WC1N 3XX"
# [10] "CB2 1AB" 
```

## Correct 1996-2010

@@

```{r}
df9610 <- df9610 %>% 
  group_by(pc, year) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(n = ifelse(pc %in% as.character(problem.pcs$pc) & year > 2003 & year <2007, NA, n))

df9610 <- pdata.frame(df9610)
predictions <- round(predict(plm(n ~ as.factor(year), effect = "individual", 
                                 model = "within", data = df9610), newdata = df9610), 2)

df9610$n[is.na(df9610$n)] <- predictions[is.na(df9610$n)]
df9610 %>% filter(pc == "M28 2SL") %>% distinct(year)
```

## Load remaining data

```{r}
df9610 <- as_tibble(df9610) %>% 
  mutate(year = as.double(as.character(year))) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>%
  group_by(year, ladcd) %>%
  summarise(n = n()) %>%            
  ungroup()

df1112 <- read_csv(data.path2011_2012) %>% 
  filter(
    #V1.domain < m,             # for multiple pc
    V1.domain == n,             # for n == 1
    year > 1995 & year <2013) %>%   
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, ladcd) %>%
  summarise(n = n()) %>%             # for n == 1  
  #summarise(n = sum(V1.domain)) %>% # for multiple pc  
  ungroup()

df <- bind_rows(df9610, df1112) %>% 
  filter(!is.na(ladcd)) %>% 
  complete(ladcd, year) %>% 
  replace(is.na(.), 0)

# tests for Scotland
# df %>% filter(substr(oa11cd, 1,1) =="S",
#               year==2010) %>% summarise(mean(n, na.rm = T))
# 
# df %>% filter(oa11cd=="S00090182")
# 
# test@data %>% filter(substr(id, 1,1) =="S",
#                      n!=0)
# 
# df %>% filter(substr(oa11cd, 1,1) =="W",
#               year==2003)
```

@@

# [reproducible results]
# Random Forest 
# 
# 5984 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4718, 4690, 5040, 4718, 5055, 4704, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE        Rsquared   MAE       
#   2     variance    0.02336229  0.8713835  0.01536402
#   2     extratrees  0.02351745  0.8698132  0.01553849
#   4     variance    0.02405073  0.8667793  0.01599751
#   4     extratrees  0.02369748  0.8716644  0.01577096
#   6     variance    0.02504045  0.8591307  0.01680305
#   6     extratrees  0.02386677  0.8708794  0.01596582
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule =
#  variance and min.node.size = 5.

@@

# [reproducible results]
# Random Forest 
# 
# 4862 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4044, 3685, 4056, 4056, 4032, 3707, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE       Rsquared   MAE      
#   2     variance    0.2004565  0.6285613  0.1460545
#   2     extratrees  0.2001702  0.6342523  0.1480880
#   4     variance    0.2080782  0.6066952  0.1503476
#   4     extratrees  0.2065532  0.6220336  0.1527747
#   6     variance    0.2099617  0.5996347  0.1507628
#   6     extratrees  0.2084788  0.6180880  0.1544252
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = extratrees and min.node.size = 5.

>>>>

```{r}
n = 1 #number of unique postcodes. 
m = 11

@@

df1112 <- read_csv(data.path2011_2012) %>% 
  filter(
    #V1.domain < m,             # for multiple pc
    V1.domain == n)             # for n == 1

df.long <- bind_rows(df9610, df1112) %>% 
  filter(year > 1995 & year < 2013) %>% 
  group_by(pc, year) %>% 
  summarise(n = n()) %>%
  ungroup() %>% 
  #arrange(desc(n)) %>% 
  pivot_wider(names_from = year, values_from = n, names_prefix = "n_") %>% 
  dplyr::select(pc, n_1996, n_1999, n_2000, n_2001, n_2002, n_2003, n_2004, n_2005, n_2006, n_2007, n_2008, n_2009, n_2010, n_2011, n_2012) %>%
  arrange(desc(n_2004), desc(n_2005)) %>% 
  slice_head(n=1000) %>% 
  pivot_longer(!pc, names_to = "year", values_to = "n") %>% 
  mutate(year = as.integer(sub("n_", "", year, fixed = TRUE))) %>% 
  replace(is.na(.), 0) %>% 
  mutate(outlier = ifelse(n > 1000 & (year==2004 | year == 2005), pc, ""))

problem.pcs <- df.long %>% filter(year==2004 | year == 2005, 
                   n > 1000) %>% 
  distinct(pc)

# n > 1500: "M28 2SL"  "SE24 9HP" "CV8 2ED"  "CW1 6GL"   
# n > 1000: SE24 9HP, CV8 2ED, GL16 7YA, CW1 6GL, M28 2SL, DE21 7BF
```

## Corrected

@@

```{r}
df.corrected <- bind_rows(df9610, df1112) %>% 
  filter(year > 1995 & year < 2013) %>% 
  group_by(pc, year) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(n = ifelse(pc %in% as.character(problem.pcs$pc) & year > 2003 & year <2007, NA, n))

df.corrected <- pdata.frame(df.corrected)
predictions <- round(predict(plm(n ~ as.factor(year), effect = "individual", 
                                 model = "within", data = df.corrected), newdata = df.corrected), 2)

df.corrected$n[is.na(df.corrected$n)] <- predictions[is.na(df.corrected$n)]
```

## LA df

```{r}
df <- df.corrected %>% 
  mutate(year = as.integer(as.character(year))) %>% 
  filter(year > 1995 & year < 2013) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, ladcd) %>%
  summarise(n = n()) %>% # for multiple pc  
  ungroup() %>% 
  complete(ladcd, year) %>% 
  filter(!is.na(ladcd)) %>% # drop c. 10 - 200 per year, which are not assigned to a LAD
  replace(is.na(.), 0) 
```

@@

# [reproducible results]
# Random Forest 
# 
# 5984 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4718, 4690, 5040, 4718, 5055, 4704, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE        Rsquared   MAE        
#   2     variance    0.01366816  0.8895425  0.009767759
#   2     extratrees  0.01350182  0.8900993  0.009603882
#   4     variance    0.01408821  0.8841051  0.010134321
#   4     extratrees  0.01354075  0.8914524  0.009664646
#   6     variance    0.01445541  0.8772260  0.010417962
#   6     extratrees  0.01369444  0.8897055  0.009772824
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = extratrees
#  and min.node.size = 5.

@@

# [reproducible results]
# Random Forest 
# 
# 4862 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4044, 3685, 4032, 4044, 4044, 3696, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE       Rsquared   MAE      
#   2     variance    0.2182933  0.5361604  0.1560099
#   2     extratrees  0.2099702  0.5660477  0.1501194
#   4     variance    0.2168118  0.5238461  0.1550630
#   4     extratrees  0.2074722  0.5590058  0.1489474
#   6     variance    0.2268891  0.5014882  0.1631466
#   6     extratrees  0.2082266  0.5503986  0.1490911
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 4, splitrule = extratrees
#  and min.node.size = 5.

### 2024-07-03 src/la_RF_corrected_10.Rmd
corrected RF v2 LA

@@

df9610 <- read_csv(data.path9610) %>% 
  filter(
      #V1.domain < m,             # for multiple pc
      V1.domain == n,             # for n == 1
      year > 1995)

@@

df1112 <- read_csv(data.path2011_2012) %>% 
  filter(
    #V1.domain < m,             # for multiple pc
    V1.domain == n)             # for n == 1

df.long <- bind_rows(df9610, df1112) %>% 
  filter(year > 1995 & year < 2013) %>% 
  group_by(pc, year) %>% 
  summarise(n = n()) %>%
  ungroup() %>% 
  #arrange(desc(n)) %>% 
  pivot_wider(names_from = year, values_from = n, names_prefix = "n_") %>% 
  dplyr::select(pc, n_1996, n_1999, n_2000, n_2001, n_2002, n_2003, n_2004, n_2005, n_2006, n_2007, n_2008, n_2009, n_2010, n_2011, n_2012) %>%
  arrange(desc(n_2004), desc(n_2005)) %>% 
  slice_head(n=1000) %>% 
  pivot_longer(!pc, names_to = "year", values_to = "n") %>% 
  mutate(year = as.integer(sub("n_", "", year, fixed = TRUE))) %>% 
  replace(is.na(.), 0) %>% 
  mutate(outlier = ifelse(n > 1000 & (year==2004 | year == 2005), pc, ""))

problem.pcs <- df.long %>% filter(year==2004 | year == 2005, 
                   n > 1000) %>% 
  distinct(pc)

# n > 1500: "M28 2SL"  "SE24 9HP" "CV8 2ED"  "CW1 6GL"   
# n > 1000: SE24 9HP, CV8 2ED, GL16 7YA, CW1 6GL, M28 2SL, DE21 7BF
```

@@

```{r}
df.corrected <- bind_rows(df9610, df1112) %>% 
  filter(year > 1995 & year < 2013) %>% 
  group_by(pc, year) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(n = ifelse(pc %in% as.character(problem.pcs$pc) & year > 2003 & year <2007, NA, n))

@@

df.corrected$n[is.na(df.corrected$n)] <- predictions[is.na(df.corrected$n)]
```

@@

```{r}
df <- df.corrected %>% 
  mutate(year = as.integer(as.character(year))) %>% 
  filter(year > 1995 & year < 2013) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, ladcd) %>%
  summarise(n = n()) %>% # for multiple pc  
  ungroup() %>% 
  complete(ladcd, year) %>% 
  filter(!is.na(ladcd)) %>% # drop c. 10 - 200 per year, which are not assigned to a LAD
  replace(is.na(.), 0) 
```

@@

@@

@@

# [reproducible results]
# Random Forest 
# 
# 5984 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4718, 4690, 5040, 4718, 5055, 4704, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE        Rsquared   MAE        
#   2     variance    0.01366816  0.8895425  0.009767759
#   2     extratrees  0.01350182  0.8900993  0.009603882
#   4     variance    0.01408821  0.8841051  0.010134321
#   4     extratrees  0.01354075  0.8914524  0.009664646
#   6     variance    0.01445541  0.8772260  0.010417962
#   6     extratrees  0.01369444  0.8897055  0.009772824
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = extratrees
#  and min.node.size = 5.

@@

path.out <- paste0(path, "/outputs/rf/figures/varimp_LA_corrected.png")
ggplot(varimp_mars) + theme_minimal() + labs(x="") #+ theme(panel.background = element_rect(fill = "white"))
ggsave(path.out)
```

@@

stopCluster(cl)
end.time <- Sys.time() 
time.taken <- round(end.time - start.time,2)
time.taken # ca. 4 minutes 
```

@@

path.out <- paste0(path, "/outputs/rf/figures/test_regions_LA_corrected.csv")
rf.year.all.metrics %>% 
  as.data.frame() %>%
  rownames_to_column(var = "metrics") %>% 
  pivot_longer(!metrics, names_to = "test.on") %>% 
  pivot_wider(names_from = metrics, values_from = value) %>% 
  left_join(lookup.region, by = c("test.on" = "RGN21CD")) %>% 
  arrange(Rsquared) %>% 
  dplyr::select(RGN21NM, Rsquared) %>% 
  rename(Region = RGN21NM) %>% 
  write_csv(path.out)
  #ggplot(aes(x = 1, y = reorder(Region, Rsquared), fill = Rsquared)) +geom_tile()

@@

# [reproducible results]
# Random Forest 
# 
# 4862 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4044, 3685, 4032, 4044, 4044, 3696, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE       Rsquared   MAE      
#   2     variance    0.2182933  0.5361604  0.1560099
#   2     extratrees  0.2099702  0.5660477  0.1501194
#   4     variance    0.2168118  0.5238461  0.1550630
#   4     extratrees  0.2074722  0.5590058  0.1489474
#   6     variance    0.2268891  0.5014882  0.1631466
#   6     extratrees  0.2082266  0.5503986  0.1490911
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 4, splitrule = extratrees
#  and min.node.size = 5.

@@

path.out <- paste0(path, "/outputs/rf/figures/varimp_LA_growth_corrected.png")
ggplot(varimp_mars) + theme_minimal() + labs(x="") #+ theme(panel.background = element_rect(fill = "white"))
ggsave(path.out)
```

@@

path.out <- paste0(path, "/outputs/rf/figures/test_regions_LA_growth_corrected.csv")
rf.year.all.metrics %>% 
  as.data.frame() %>%
  rownames_to_column(var = "metrics") %>% 
  pivot_longer(!metrics, names_to = "test.on") %>% 
  pivot_wider(names_from = metrics, values_from = value) %>% 
  left_join(lookup.region, by = c("test.on" = "RGN21CD")) %>% 
  arrange(Rsquared) %>% 
  dplyr::select(RGN21NM, Rsquared) %>% 
  rename(Region = RGN21NM) %>% 
  write_csv(path.out)
  #ggplot(aes(x = 1, y = reorder(Region, Rsquared), fill = Rsquared)) +geom_tile()

>>>>

I use the problem postcodes from n = 1 as these are the true outliers as per the
line plots.

@@

df9610 <- read_csv(data.path9610) %>% 
  filter(
      V1.domain < m,               # for multiple pc
      #V1.domain == n,             # for n == 1
      year > 1995)

@@

df1112 <- read_csv(data.path2011_2012) %>% 
  filter(
    V1.domain < m)               # for multiple pc
    #V1.domain == n)             # for n == 1

df.long <- bind_rows(df9610, df1112) %>% 
  filter(year > 1995 & year < 2013) %>% 
  group_by(pc, year) %>% 
  summarise(n = sum(V1.domain)) %>%
  ungroup() %>% 
  #arrange(desc(n)) %>% 
  pivot_wider(names_from = year, values_from = n, names_prefix = "n_") %>% 
  dplyr::select(pc, n_1996, n_1999, n_2000, n_2001, n_2002, n_2003, n_2004, n_2005, n_2006, n_2007, n_2008, n_2009, n_2010, n_2011, n_2012) %>%
  arrange(desc(n_2004), desc(n_2005)) %>% 
  slice_head(n=1000) %>% 
  pivot_longer(!pc, names_to = "year", values_to = "n") %>% 
  mutate(year = as.integer(sub("n_", "", year, fixed = TRUE))) %>% 
  replace(is.na(.), 0) %>% 
  mutate(outlier = ifelse(n > 1000 & (year==2004 | year == 2005), pc, ""))

# From n = 1 as these are the 'true' outliers
problem.pcs <- c("SE24 9HP", "CV8 2ED", "GL16 7YA", "CW1 6GL", "M28 2SL", "DE21 7BF")
```

@@

```{r}
df.corrected <- bind_rows(df9610, df1112) %>% 
  filter(year > 1995 & year < 2013) %>% 
  group_by(pc, year) %>% 
  summarise(n = sum(V1.domain)) %>% 
  ungroup() %>% 
  # The next line is different than the same for  n = 1: problem.pcs$pc
  mutate(n = ifelse(pc %in% as.character(problem.pcs) & year > 2003 & year <2007, NA, n))

@@

df.corrected$n[is.na(df.corrected$n)] <- predictions[is.na(df.corrected$n)]

@@

```{r}
df <- df.corrected %>% 
  mutate(year = as.integer(as.character(year))) %>% 
  filter(year > 1995 & year < 2013) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, ladcd) %>%
  summarise(n = sum(n)) %>% # for multiple pc  
  ungroup() %>% 
  complete(ladcd, year) %>% 
  filter(!is.na(ladcd)) %>% # drop c. 10 - 200 per year, which are not assigned to a LAD
  replace(is.na(.), 0) 
```

@@

# detectCores()
# cl <- makePSOCKcluster(14)
# registerDoParallel(cl)

@@

#stopCluster(cl)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken

@@

# [reproducible results]
# Random Forest 
# 
# 5984 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4718, 4690, 5040, 4718, 5055, 4704, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE       Rsquared   MAE      
#   2     variance    0.1881989  0.7750790  0.1223893
#   2     extratrees  0.1944376  0.7543149  0.1274344
#   4     variance    0.1906884  0.7730657  0.1256452
#   4     extratrees  0.1930998  0.7596818  0.1276155
#   6     variance    0.1937399  0.7677967  0.1282843
#   6     extratrees  0.1927437  0.7608415  0.1277447
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = variance and
#  min.node.size = 5.

@@

path.out <- paste0(path, "/outputs/rf/figures/varimp_LA_corrected_10.png")
ggplot(varimp_mars) + theme_minimal() + labs(x="") #+ theme(panel.background = element_rect(fill = "white"))
ggsave(path.out)
```

@@

# stopCluster(cl)
end.time <- Sys.time() 
time.taken <- round(end.time - start.time,2)
time.taken # ca. 4 minutes 
```

@@

path.out <- paste0(path, "/outputs/rf/figures/test_regions_LA_corrected_10.csv")
rf.year.all.metrics %>% 
  as.data.frame() %>%
  rownames_to_column(var = "metrics") %>% 
  pivot_longer(!metrics, names_to = "test.on") %>% 
  pivot_wider(names_from = metrics, values_from = value) %>% 
  left_join(lookup.region, by = c("test.on" = "RGN21CD")) %>% 
  arrange(Rsquared) %>% 
  dplyr::select(RGN21NM, Rsquared) %>% 
  rename(Region = RGN21NM) %>% 
  write_csv(path.out)
  #ggplot(aes(x = 1, y = reorder(Region, Rsquared), fill = Rsquared)) +geom_tile()

@@

# [reproducible results]
# Random Forest 
# 
# 4862 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4044, 3685, 4032, 4044, 4044, 3696, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE       Rsquared   MAE      
#   2     variance    0.2773324  0.6169393  0.2025296
#   2     extratrees  0.2692856  0.6437281  0.1982852
#   4     variance    0.2836790  0.5992575  0.2060827
#   4     extratrees  0.2717096  0.6339425  0.2004439
#   6     variance    0.2899917  0.5806674  0.2100017
#   6     extratrees  0.2755481  0.6223759  0.2037709
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = extratrees
#  and min.node.size = 5.

@@

path.out <- paste0(path, "/outputs/rf/figures/varimp_LA_growth_corrected_10.png")
ggplot(varimp_mars) + theme_minimal() + labs(x="") #+ theme(panel.background = element_rect(fill = "white"))
ggsave(path.out)
```

@@

path.out <- paste0(path, "/outputs/rf/figures/test_regions_LA_growth_corrected_10.csv")
rf.year.all.metrics %>% 
  as.data.frame() %>%
  rownames_to_column(var = "metrics") %>% 
  pivot_longer(!metrics, names_to = "test.on") %>% 
  pivot_wider(names_from = metrics, values_from = value) %>% 
  left_join(lookup.region, by = c("test.on" = "RGN21CD")) %>% 
  arrange(Rsquared) %>% 
  dplyr::select(RGN21NM, Rsquared) %>% 
  rename(Region = RGN21NM) %>% 
  write_csv(path.out)
  #ggplot(aes(x = 1, y = reorder(Region, Rsquared), fill = Rsquared)) +geom_tile()

### 2024-07-03 src/oa_RF_corrected.Rmd
corrected RF v2 LA

```{r}
df9610 <- df9610 %>% 
  group_by(pc, year) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(n = ifelse(pc %in% as.character(problem.pcs$pc) & year > 2003 & year <2007, NA, n))

df9610 <- pdata.frame(df9610)
predictions <- round(predict(plm(n ~ as.factor(year), effect = "individual", 
                                 model = "within", data = df9610), newdata = df9610), 2)

df9610$n[is.na(df9610$n)] <- predictions[is.na(df9610$n)]
df9610 %>% filter(pc == "M28 2SL") %>% distinct(year)
```

## Load remaining data

```{r}
df9610 <- as_tibble(df9610) %>% 
  mutate(year = as.double(as.character(year))) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>%
  group_by(year, oa11cd) %>%
  summarise(n = n()) %>%            
  ungroup()

df1112 <- read_csv(data.path2011_2012) %>% 
  filter(
    #V1.domain < m,             # for multiple pc
    V1.domain == n,             # for n == 1
    year > 1995 & year <2013) %>%   
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, oa11cd) %>%
  summarise(n = n()) %>%             # for n == 1  
  #summarise(n = sum(V1.domain)) %>% # for multiple pc  
  ungroup()

df <- bind_rows(df9610, df1112) %>% 
  filter(!is.na(oa11cd)) %>% 
  complete(oa11cd, year) %>% 
  replace(is.na(.), 0)

# tests for Scotland
# df %>% filter(substr(oa11cd, 1,1) =="S",
#               year==2010) %>% summarise(mean(n, na.rm = T))
# 
# df %>% filter(oa11cd=="S00090182")
# 
# test@data %>% filter(substr(id, 1,1) =="S",
#                      n!=0)
# 
# df %>% filter(substr(oa11cd, 1,1) =="W",
#               year==2003)
```

@@

# stopCluster(cl)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken #20.6h

@@

# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 2926910, 2926924, 3136005, 2926924, 3136005, 2926924, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE     
#   2     variance    4.999920  0.2053697  1.047293
#   2     extratrees  5.167655  0.1540213  1.103048
#   5     variance    5.187039  0.1710128  1.034382
#   5     extratrees  5.169570  0.1557868  1.122845
#   8     variance    5.633427  0.1247189  1.035171
#   8     extratrees  5.182860  0.1563555  1.137332
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule =
#  variance and min.node.size = 5.

@@

path.out <- paste0(path, "/outputs/rf/figures/varimp_OA_corrected.csv")
write_csv(varimp_mars, path.out)

# ffsmodel_LLO <- ffs(predictors = df[, c("area", "dist", "dist.retail", "London", "south",  
#                                       "n.slag", "n.lag", "n.l.slag", "n.nearest.city", 
#                                                         "year")], 
#                     response = df$n, #%>% dplyr::select(n) %>% as.data.frame %>% mutate(n = as.numeric(n)),
#                     trControl = tc,
#                     method = "ranger",
#                     #na.action = na.omit,
#                     #importance = "impurity",
#                     metric="Rsquared",
#                     verbose=FALSE)
# ffsmodel_LLO
# ffsmodel_LLO$selectedvars
# plot_ffs(ffsmodel_LLO)
```

>>>>

```{r}
df.corrected <- bind_rows(df9610, df1112) %>% 
  filter(year > 1995 & year < 2013) %>% 
  group_by(pc, year) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(n = ifelse(pc %in% as.character(problem.pcs$pc) & year > 2003 & year <2007, NA, n))

df.corrected <- pdata.frame(df.corrected)
predictions <- round(predict(plm(n ~ as.factor(year), effect = "individual", 
                                 model = "within", data = df.corrected), newdata = df.corrected), 2)

df.corrected$n[is.na(df.corrected$n)] <- predictions[is.na(df.corrected$n)]
```

## OA df

```{r}
df <- df.corrected %>% 
  mutate(year = as.integer(as.character(year))) %>% 
  filter(year > 1995 & year < 2013) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, oa11cd) %>%
  summarise(n = n()) %>% # for multiple pc  
  ungroup() %>% 
  complete(oa11cd, year) %>% 
  filter(!is.na(oa11cd)) %>% # drop c. 10 - 200 per year, which are not assigned to a LAD
  replace(is.na(.), 0) 
```

@@

# stopCluster(cl)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken #20.16h

@@

# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 2926910, 2926924, 3136005, 2926924, 3136005, 2926924, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE      
#   2     variance    2.307827  0.2770946  0.7497850
#   2     extratrees  2.329867  0.2306295  0.7719781
#   5     variance    2.432873  0.2744482  0.7596487
#   5     extratrees  2.409776  0.2344573  0.7960409
#   8     variance    2.486179  0.2616929  0.7571522
#   8     extratrees  2.452737  0.2318285  0.8086679
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = variance and min.node.size = 5.

@@

path.out <- paste0(path, "/outputs/rf/figures/varimp_OA_corrected.csv")
varimp_mars$importance %>% 
  rownames_to_column() %>%
  rename(variable = rowname,
         importance = Overall) %>% 
  write_csv(path.out)
```

THE BELLOW HAS NOT BEEN RUN NEITHER THE FILENAMES HAS BEEN CHANGED (add: _corrected)
